\textit{Urban and building multiscale co-simulation: case study implementations on two university campuses}

### 2016-04-25 latex/UMEM_CoSim.tex
Fixed a bunch of stuff Daren suggested

% tBPSguide.tex
% v2.1 released November 2014

@@

\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage{subfigure}% Support for small, `sub' figures and tables
\usepackage{lmodern}
\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{lineno}

@@

\begin{abstract}
    This paper describes the co-simulation process of the building and urban scale models of two campuses of higher education buildings in Switzerland. The campuses are modeled at both the building scale using the EnergyPlus simulation engine and at the urban scale using the CitySim engine. A co-simulation framework is used to execute simulations from both engines concurrently with an exchange of information to leverage the various strengths of each. In the first case study, on-site weather and measured performance data is then compared to the output from two modeling scenarios: building-scale simulation using EnergyPlus and co-simulation of the engines. A partial calibration process is implemented to reconcile the simulations with the measured data \noteDT{insert: "of"} a targeted office building on campus. In the second case study, the co-simulation results are compared to the both the CitySim simulation and EnergyPlus engines. The results show that {\color{red}insert results here}. A discussion is included of the challenges encountered with the urban scale calibration and the strengths and weaknesses of the developed process.\noteDT{Clayton, can you get your editor to do hard linewrapping? all your paragraphs are a single line which breaks the diff model of GitHub and makes editing in VIM super hard...}
\end{abstract}

@@

The CitySim simulation engine is an example of such a program designed and optimized for urban-scale simulation. CitySim is an urban performance simulation engine that comprises a Solver module as well as a graphical user interface. It focuses on the energy flows of multiple simplified building models and their interdependent relationship with their urban climate \citep{Robinson:2009tm}. CitySim includes building thermal, urban radiation, occupant behavior, and plant/equipment models integrated as a single simulation engine. CitySim simulates multiple buildings up to city scale using simplified models in order to achieve a good compromise between modeling accuracy, computational overheads and data availability. Each building's thermal behavior is based on an electrical analogy using a two node resistor-capacitor network. The internal lighting, people, and miscellaneous loads are modeled using a simplified occupancy-based approximation. The heating, ventilation, and air-conditioning (HVAC) systems are modeled using a single equation that approximates the total mass flow rate required to meet the sensible and latent loads of each building as a whole. Each of these simplifying approximations empowers the urban-scale simulation to have reasonable execution times with respect to the number of buildings being simulated.

@@

Both building and urban-scale simulation domains have rightfully chosen boundary conditions that reflect their key goals while seeking to minimize the input parameters necessary and run-times of the engines themselves. This focus results in certain deficiencies with respect to modeling various phenomenon. For example, urban scale simulation highly simplifies the building systems and internal load models, thus making retrofit analysis at the systems level difficult. And whole building simulation neglects many of the various contextual consideration of the urban environment such as long wave radiation exchange with adjacent surfaces and localized urban weather effects.\noteDT{ref?}

In order to address the deficiencies of the individual engines, the current effort described\noteDT{can we do phrasing? prettyplease?} seeks to couple building and urban scale simulation. The research in this paper is part of an\noteDT{s/an/a/} larger coupling effort in which various engines are connected and co-simulated to create a more comprehensive analysis of the urban scale \citep{Dorer:2013vt,Allegrini:2012kx}. The target is the computational interface between the building energy model, using EnergyPlus, and the urban energy model using CitySim. An overview of the larger scope is shown in Figure \ref{fig:UMEM} and the context of the coupling task is shown as the interface between the City Energy Simulation (CES) model and the Building Energy Simulation (BES) model.

The coupling and co-simulation process is implemented on two case studies in Switzerland. The first case study is the ETH Z\"urich Hoenggerberg campus in Z\"urich, Switzerland. The campus was modeled in the CitySim simulation engine and co-simulated using work-flow automation. The target of this case study is to evaluate the differences between the coupled and uncoupled EnergyPlus simulation results with a target on the use of these models for building retrofit analysis.\noteDT{I do not understand the preceding sentence. Neither will the reviewer} This scenario includes the use of measured data for heating and cooling within their respective seasons to compare to the simulation results. The second case study is the EPFL campus in Lausanne, Switzerland. The objective of this scenario is to evaluate the differences between coupled and uncoupled versions of the CitySim simulation engine.

@@

This paper describes the achievement of several objectives:
\begin{enumerate}
  \item Automation of the process of simultaneous meta-data extraction from a building information model (BIM) for the creation of both building and urban-scale performance models for a real-world campus of buildings
  \item Co-simulate the urban and building scale models through concurrent information exchange
  \item Implement a simplified calibration procedure based on reconciling the co-simulation output results for a target building that have\noteDT{s/have/has/} adequate measured energy performance data from the campus energy information system (EIS) 
\end{enumerate}

The first two objectives have been demonstrated in a simplified context in previous literature \citep{thomas2014multiscale,Miller:2015vk}. The innovation in the current publication is an extension to this research through the modelling and co-simulation of real-world case studies. With respect to the third contribution, to the best of the author's knowledge, no previous study has compared the results of a building and urban-scale co-simulation procedure to measured data from a real-world campus.\noteDT{:)}

\subsection{Previous multi-scale coupling studies}
Previous attempts of information exchange have been implemented between simulation engines at various scales. Much of the initial co-simulation work in the literature is at the subsystem and building-scales. Previous studies have analyzed strong and loose coupling of engines at this scale \citep{Trcka:2010cr,Wetter:2011kh}. Coupling of building-scale simulation with urban-scale computational fluid dynamics (CFD) is attempted for modeling natural ventilation \citep{Zhang:2013vx} and to improve energy prediction \citep{Bouyer:2011eha}. A comprehensive review of energy and airflow modeling of neighborhoods and university campuses was published that includes strategies\noteDT{did you mean: "strategic"?} aspects of coupling different types of models \citep{Srebric:2015gq}. EnergyPlus has been coupled with ENVI-met, a micro-climate computational fluid dynamics (CFD) program \citep{Yang:2012cr}. It was also coupled with simplified lumped parameter models in order to facilitate comparison with measured sensor data \citep{Martin:2015fj}. EnergyPlus and the TEP Urban Canopy Model program were coupled in order to quantify the influences of urban localized weather effects on whole building simulation \citep{Bueno:2011hi} and urban weather generation \citep{Bueno:2013hh}. Recent work in coupling geographic information systems platforms like GIS and simplified performance modeling techniques have also been completed \citep{Fonseca:2015bm}\noteDT{this is not technically a simulation coupling}.
% \subsection{Urban scale performance simulation}

@@

\subsection{Coupling process}
The coupling process of a simplified single zone model and contextual surrounding buildings is outlined in previous studies \citep{thomas2014multiscale,Thomas:2012wj}\noteDT{not sure the second reference includes coupling...}. This study forms the basis for the methodology in the current effort. This process utilizes the Design Performance Viewer (DPV) and associated work flow. The DPV is a tool written to extract and simulate an EnergyPlus input data file (IDF) from an Autodesk\textsuperscript{TM} Revit\textsuperscript{TM} BIM \citep{Schlueter2009}. The main philosophy behind the tool is rapid simulation of the building information model from the earliest design possible and can be used throughout the life-cycle of the building including retrofit analysis \citep{Miller:2014tu}. This process is achieved by augmenting the information in the BIM with default values and abstracting information not relevant for energy simulation. The tool already has a simplified notion of surrounding buildings, which are modeled in the BIM as simple mass objects without further information and are exported as shading surfaces to EnergyPlus. This functionality is used for creating the CitySim mass scene and leads to a crude model of the urban context of the building. The existing DPV philosophy of allowing the designer to iterate rapidly on early design decisions based on feedback about the performance of the design remains. This approach includes streamlining the process where running a simulation requires no effort from the designer due to automatic creation of input files, execution and analysis of the results.

@@

% On an hourly basis, CitySim performs a heating and cooling needs prediction step. The temperature determination step for the main building is replaced with the results of the EnergyPlus timestep as obtained through FMI library. The FMI library is used to send climatic and occupational data from CitySim to EnergyPlus, and to receive data from EnergyPlus that are further used within CitySim for the next time steps. 
Several key urban-scale weather variables are sent to EnergyPlus from CitySim in order to better account for the localized effects of surrounding buildings, geography and climactic\noteDT{s/climactic/climatic/} conditions. These variables include various outdoor air conditions such as drybulb and wetbulb temperatures, dewpoint, humidity, wind speed and direction, and direct and diffuse solar radiation. These variables overwrite the input weather variables that EnergyPlus obtains from its weather file input. One of the key objectives of CitySim as a a\noteDT{s/a a/a/} simulation engine has been its to account for physical phenomenon inherent to urban environments that is often neglected in building-scale simulation environments \citep{Robinson:2004cr,Robinson:2009tm}.\noteDT{this sentence, man. i can't even} Long wave radiation exchange between the simulated building and its surroundings is sent to EnergyPlus; this process is describe\noteDT{s/describe/described/} in detail in a subsequent methodology section\noteDT{can we not just name the section? this phrasing seems awkward}. Finally, CitySim shares its calculated occupancy schedules as it uses a more robust model of occupants behavior \citep{Haldi:2011dr}.

@@

Variables sent to CitySim by EnergyPlus at each time step include several variables related to the calculation of heating and cooling loads of a targeted building. These variables are transferred due to the ability of EnergyPlus to model more detailed building systems, schedules, ventilation and internal load types than CitySim. For example, EnergyPlus is flexible enough to model a detailed, radiant heating and cooling system that would be impossible in CiytSim \noteDT{add parenthesis to citation}}\cite{barbara:2015tz}. EnergyPlus is an engine optimized on\noteDT{I'm not sure this is proper English. Or American for that matter...} the accuracy of building-scale systems, thus CitySim can take advantage of these models through coupling and co-simulation. EnergyPlus sends the heating and cooling loads, the surface temperatures of the exterior surfaces and the ventilation flow rates to CitySim.

@@

In comparison, CitySim calculates LWR exchange by calculating an aggregated equivalent temperature, $T_{env}$, and radiative heat transfer coefficient, $h_{r,env}$, from surrounding urban surfaces in addition to ground, sky, and air \citep{Robinson:2009tm}. The calculation for $T_{env}$ is expressed in Equation \ref{CitySim_Tenv} with the $F$ values being view factors of the surrounding environment including adjacent surfaces $i=1..n$. $h_{r,env}$ is based on a first order Talyor development of the numerator of Equation \ref{EPlus_h} around $(T_{surf}+T_{variable})/2$ and therefore $Q_{LWR,CitySim}$ is calculated using Equation \ref{CitySim_LWR_Ext}.
\begin{equation} \label{CitySim_Tenv} 
\sigma T_{env}^4 = \sigma F_{sky}T_{sky}^4 +\sigma F_{grd}T_{grd}^4 + \sum_{i=1}^{n} \epsilon_i \sigma F_{i}T_{i}^4
\end{equation}
\begin{equation} \label{CitySim_LWR_Ext} 
Q_{LWR,CitySim} = h_{r,env}(T_{surf}-T_{env})
\end{equation}

@@

\subsection{Work flow automation}
The coupling, simulation and co-simulation process is completely managed within a program called VisTrails \citep{Anonymous:Cayf2tu7}. This tool empowers the coupling of various executable files and their connecting scripts in \noteDT{deleted: "a"} graphical diagrams that enhances reproducibility and process automation \citep{Freire:2014tt}.

INSERT VISTRAILS GRAPHIC HERE\noteCM{Daren -- can you give me a good screenshot of the Vistrails for the HPI building? Pretty please.}\noteDT{sure - check out 36-HPI-cosim.pdf in the figures folder}

\subsection{Simplified calibration}
In the first case study, one aspect of this analysis is the comparison of actual measured performance of a buildings\noteDT{s/buildings/building/} on campus with the simulation results of the co-simulation. A simplified calibration procedure is adapted from previous research to compare the measured heating and cooling data available on campus with various simulation scenarios \citep{Samuelson:2015jg}. This calibration procedure was utilized in the performance reconciliation of 18 buildings that were built according to the LEED Canada protocol and were under review of actualized performance. This protocol is unique in its analysis process to uncover design model deficiencies in a step-wise manner, utilizing the most easily accessible knowledge first and working towards equilibrium between measured and simulated. An appropriate balance between effort of implementation and value generated through the calibration process.

@@

\subsection{Campus case study 1: ETHZ Hoenggerberg Campus}
% {\color{red}This section will describe the ETH Hoenggerberg case study}
%The simulation and calibration process is implemented on a campus case study located in Z\"urich, Switzerland. 
The ETH Z\"urich Hoenggerberg campus includes 32 higher education \noteDT{deleted: "buildings"} with spaces allocated to laboratories, office space, lecture halls, cafeterias, data centers and other types of similar spaces. The campus has a centralized energy management system (EMS) that contains 807 energy and water measurement points from heating, cooling, electricity, city gas, domestic hot water, grey water, and general water consumption.

@@

The focus of the co-simulation process is that the performance of a targeted building is evaluated through solo and coupled methods. The HPI building on campus was chosen in this case study due to \noteDT{insert: "the"} amount and quality of measured data available from the EMS for this building. HPI is a 2,610 sq. meter building that \noteDT{insert: "is"} made up mostly of office space and classrooms. It also includes 400 sq. meter\noteDT{can we use $m^2$ instead?} convenience store and coffee shop. The building is indicated on a campus map shown in Figure \ref{fig:campusmap} and is shaded red.

@@

\subsection{Model development}
In order to perform a co-simulation of the targeted buildings, initially a CitySim model of the campus is developed. Through the workflow automation process, this geometry was converted into an EnergyPlus input file as seen in Figure \ref{fig:HPIcampus}. The EnergyPlus input file is then used as an input to execute EnergyPlus solo and co-simulation processes for the purpose of simplified calibration, and then to understand the magnitude of difference between these simulation scenarios.
% An existing EnergyPlus model is used for the HPZ building and simplified single-zone EnergyPlus models are extracted from the CitySim geometry for the other three targeted buildings.

@@

Energy data from the HPI building was collected and analyzed in the context of the simplified calibration procedures. The measured datasets are screened and aggregated into typical usage profiles to be used for the lighting, plug-loads, and HVAC equipment availability schedules and power densities. Figure \ref{fig:hpi_elec_profiles} illustrates the aggregation examples of electrical energy for the HPI building. This profile was created through a filtering and clustering process known as \emph{DayFilter} \citep{Miller:2015kr}. This profile is used to set the availability schedules as inputs into the EnergyPlus simulation to emulate the way occupants inhabit the building and how the building management system (BMS) controls the lighting and HVAC systems. This approach is compared to the practice of interviews and site visits to determine such input parameters.\noteDT{where??? how??? i don't get it...}

@@

The measured and simulated data from both the co-simulation and EnergyPlus solo simulation was compared in order to create a realistic scenario for comparison. The calibration process was undertaken through a series of steps such as including local weather conditions for the simulation period and adding custom lighting schedules and power densities extracted from the measured data. The models were calibrated to the summer season (May-September) for cooling and the winter season (Jan-April and October to December) for heating. This approach was taken as the data quality for the measurements were deemed most accurate during the appropriate seasons. Figure \ref{fig:hpi_measvssim} illustrates a comparison of the measured data with the simulations after the tuning process. The final calibrated EnergyPlus solo model had a normalized mean bias error (NMBE) of -9.36\% and a coefficient of variation of root mean square error (CVRMSE) of 21.7\% for cooling and -9.36\% and 29.4\% for heating. These metrics fall within the +/-10\% NMBE and +/-30\% CVRSME used in this case study for the purposes of partial calibration. The goal of calibration in this case is to simply bring the models to within a reasonable range of reality in order to bring more confidence to analysis of the discrepancies between the solo and co-simulation scenarios.\noteDT{Clayton, can you introduce a consistency in the symbols for the figures? say, squares for co-simulation, circles for e+, triangles for measured? and do this across all the figures? small detail, but i think shows quality and a certain, how shall i call it? swissness? a qualité suisse?}
%Daily data was used to calculated goodness of fit to determine calibration success. 
%The final calibrated EnergyPlus solo model had a normalized mean bias error (NMBE) of -9.36\% and a coefficient of variation of root mean square error (CVRMSE) of 21.7\% for cooling and -9.36\% and 29.4\% for heating.

@@

\subsection{EnergyPlus co-simulation results}

After calibration, a comparison of co-simulation and solo EnergyPlus simulations is made. For cooling, a discrepancy can be seen between co-simulation and solo EnergyPlus. A 20.2\% decrease in \noteDT{with respect to what???} predicted cooling energy is observed as seen in Figure \ref{fig:hpi_energypluscooling}. Figure \ref{fig:hpi_energyplusheating} illustrates the difference in predicted heating energy consumption across the test year. A consistent offset exists across the time frame of days in January, the peak of the heating season. A more varied discrepancy across the heating months is noticed resulting and\noteDT{s/and/in an/} overall increase of heating prediction of 4.8\% due to co-simulation. The exchange of long wave radiation for this particular site is likely greater due to \noteDT{greater than what??} the proximity of surrounding buildings. These performance differences due to co-simulation are compared to a theoretical single-zone case study in which there was a 15-30\% increase in heating energy and a 4-11\% decrease in cooling energy. The results form\noteDT{s/form/from/} this\noteDT{which?} scenario are less extreme from the heating side and more extreme from\noteDT{from, from, from, you know what? there has to be a better way to formulate this sentence} the cooling side.

@@

With a particularly strong visual and formal identity, the SwissTech Convention Centre (STCC) is clearly the key protagonist.\noteDT{move main sentence to start of paragraph} Applied with important functions for the region, the building has definitely become the new landmark. Designed as a Minergie\noteDT{ref?} building, it includes modern energy conversion technologies to reduce its energy consumption. The focus of the co-simulation is realised on the STCC, simulated with the nearby buidings for housing, retail and service areas.

>>>>

% tBPSguide.tex v2.1 released November 2014

@@

\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage{subfigure}% Support for small, `sub' figures and tables
\usepackage{lmodern}
\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{lineno}
\RequirePackage{fix-cm}

@@

\begin{abstract}
    This paper describes the co-simulation process of the building and urban
    scale models of two campuses of higher education buildings in Switzerland.
    The campuses are modeled at both the building scale using the EnergyPlus
    simulation engine and at the urban scale using the CitySim engine. A co-
    simulation framework is used to execute simulations from both engines
    concurrently with an exchange of information to leverage the various
    strengths of each. In the first case study, on-site weather and measured
    performance data is then compared to the output from two modeling
    scenarios: building-scale simulation using EnergyPlus and co-simulation of
    the engines. A partial calibration process is implemented to reconcile the
    simulations with the measured data of a targeted office building on
    campus. In the second case study, the co-simulation results are compared
    to the both the CitySim simulation and EnergyPlus engines. The results
    show that {\color{red}insert results here}. A discussion is included of
    the challenges encountered with the urban scale calibration and the
    strengths and weaknesses of the developed process.
    % \noteDT{Clayton, can you
    % get your editor to do hard linewrapping? all your paragraphs are a single
    % line which breaks the diff model of GitHub and makes editing in VIM super
    % hard...}
\end{abstract}

@@

The CitySim simulation engine is an example of such a program designed and
optimized for urban-scale simulation. CitySim is an urban performance
simulation engine that comprises a Solver module as well as a graphical user
interface. It focuses on the energy flows of multiple simplified building
models and their interdependent relationship with their urban climate
\citep{Robinson:2009tm}. CitySim includes building thermal, urban radiation,
occupant behavior, and plant/equipment models integrated as a single
simulation engine. CitySim simulates multiple buildings up to city scale using
simplified models in order to achieve a good compromise between modeling
accuracy, computational overheads and data availability. Each building's
thermal behavior is based on an electrical analogy using a two node resistor-
capacitor network. The internal lighting, people, and miscellaneous loads are
modeled using a simplified occupancy-based approximation. The heating,
ventilation, and air-conditioning (HVAC) systems are modeled using a single
equation that approximates the total mass flow rate required to meet the
sensible and latent loads of each building as a whole. Each of these
simplifying approximations empowers the urban-scale simulation to have
reasonable execution times with respect to the number of buildings being
simulated.

@@

Both building and urban-scale simulation domains have rightfully chosen
boundary conditions that reflect their key goals while seeking to minimize the
input parameters necessary and run-times of the engines themselves. This focus
results in certain deficiencies with respect to modeling various phenomenon.
For example, urban scale simulation highly simplifies the building systems and
internal load models, thus making retrofit analysis at the systems level
difficult. And whole building simulation in EnergyPlus neglects many of the
various contextual consideration of the urban environment such as long wave
radiation exchange with adjacent surfaces and localized urban weather effects
\citep{Lawrie:2001vf}.%\noteDT{ref?}

In order to address the deficiencies of the individual engines, the current
effort seeks to couple building and urban scale simulation. The research in
this paper is part of an\noteDT{s/an/a/} larger coupling effort in which
various engines are connected and co-simulated to create a more comprehensive
analysis of the urban scale \citep{Dorer:2013vt,Allegrini:2012kx}. The target
is the computational interface between the building energy model, using
EnergyPlus, and the urban energy model using CitySim. An overview of the
larger scope is shown in Figure \ref{fig:UMEM} and the context of the coupling
task is shown as the interface between the City Energy Simulation (CES) model
and the Building Energy Simulation (BES) model.

% \noteDT{can we do phrasing? prettyplease?}

The coupling and co-simulation process is implemented on two case studies in
Switzerland. The first case study is the ETH Z\"urich Hoenggerberg campus in
Z\"urich, Switzerland. The campus was modeled in the CitySim simulation engine
and co-simulated using work-flow automation. The target of this case study is
to evaluate the differences between the coupled and solo EnergyPlus
simulations based on the variables exchanged. This scenario includes the use
of measured data for heating and cooling within their respective seasons to
compare to the simulation results. The second case study is the EPFL campus in
Lausanne, Switzerland. The objective of this scenario is to evaluate the
differences between coupled and uncoupled versions of the CitySim simulation
engine.

 % with a target on the use of these models for building retrofit analysis.\noteDT{I do not understand the preceding sentence. Neither will the reviewer}

@@

This paper describes the achievement of several objectives:
\begin{enumerate}
  \item Automation of the process of simultaneous meta-data extraction from a
  building information model (BIM) for the creation of both building and
  urban-scale performance models for a real-world campus of buildings
  \item Co-simulate the urban and building scale models through concurrent information exchange
  \item Implement a simplified calibration procedure based on reconciling the
  co-simulation output results for a target building using measured energy
  performance data from the campus energy information system (EIS)
\end{enumerate}

% \noteDT{s/have/has/}

The first two objectives have been demonstrated in a simplified context in
previous literature \citep{thomas2014multiscale,Miller:2015vk}. The innovation
in the current publication is an extension to this research through the
modelling and co-simulation of real-world case studies. With respect to the
third contribution, to the best of the authors' knowledge, no previous study
has compared the results of a building and urban-scale co-simulation procedure
to measured data from a real-world campus.% \noteDT{:)}

\subsection{Previous multi-scale coupling studies}
Previous attempts of information exchange have been implemented between
simulation engines at various scales. Much of the initial co-simulation work
in the literature is at the subsystem and building-scales. Previous studies
have analyzed strong and loose coupling of engines at this scale
\citep{Trcka:2010cr,Wetter:2011kh}. Coupling of building-scale simulation with
urban-scale computational fluid dynamics (CFD) is attempted for modeling
natural ventilation \citep{Zhang:2013vx} and to improve energy prediction
\citep{Bouyer:2011eha}. A comprehensive review of energy and airflow modeling
of neighborhoods and university campuses was published that includes
strategic aspects of coupling different %\noteDT{did you mean: "strategic"?}b
types of models \citep{Srebric:2015gq}. EnergyPlus has been coupled with ENVI-
met, a micro-climate computational fluid dynamics (CFD) program
\citep{Yang:2012cr}. It was also coupled with simplified lumped parameter
models in order to facilitate comparison with measured sensor data
\citep{Martin:2015fj}. EnergyPlus and the TEP Urban Canopy Model program were
coupled in order to quantify the influences of urban localized weather effects
on whole building simulation \citep{Bueno:2011hi} and urban weather generation
\citep{Bueno:2013hh}.
% Recent work in coupling geographic information systems platforms like GIS and simplified performance modeling techniques have also been completed \citep{Fonseca:2015bm}\noteDT{this is not technically a simulation coupling}.
% \subsection{Urban scale performance simulation}

@@

\subsection{Coupling process} The coupling process of a simplified single zone
model and contextual surrounding buildings is outlined in previous studies
\citep{thomas2014multiscale}. This study forms the basis for the methodology
in the current effort. This process utilizes the Design Performance Viewer
(DPV) and associated work flow. The DPV is a tool written to extract and
simulate an EnergyPlus input data file (IDF) from an
Autodesk\textsuperscript{TM} Revit\textsuperscript{TM} BIM
\citep{Schlueter2009}. The main philosophy behind the tool is rapid simulation
of the building information model from the earliest design possible and can be
used throughout the life-cycle of the building including retrofit analysis
\citep{Miller:2014tu}. This process is achieved by augmenting the information
in the BIM with default values and abstracting information not relevant for
energy simulation. The tool already has a simplified notion of surrounding
buildings, which are modeled in the BIM as simple mass objects without further
information and are exported as shading surfaces to EnergyPlus. This
functionality is used for creating the CitySim mass scene and leads to a crude
model of the urban context of the building. The existing DPV philosophy of
allowing the designer to iterate rapidly on early design decisions based on
feedback about the performance of the design remains. This approach includes
streamlining the process where running a simulation requires no effort from
the designer due to automatic creation of input files, execution and analysis
of the results.% \noteDT{not sure the second reference includes coupling...}

@@

% On an hourly basis, CitySim performs a heating and cooling needs prediction step. The temperature determination step for the main building is replaced with the results of the EnergyPlus timestep as obtained through FMI library. The FMI library is used to send climatic and occupational data from CitySim to EnergyPlus, and to receive data from EnergyPlus that are further used within CitySim for the next time steps. 
Several key urban-scale weather variables are sent to EnergyPlus from CitySim
in order to better account for the localized effects of surrounding buildings,
geography and climate conditions. These variables include various outdoor air
conditions such as drybulb and wetbulb temperatures, dewpoint, humidity, wind
speed and direction, and direct and diffuse solar radiation. These variables
overwrite the input weather variables that EnergyPlus obtains from its weather
file input. CitySim is designed to account for physical phenomenon inherent to
urban environments, that are often neglected in building-scale simulation
environments \citep{Robinson:2004cr,Robinson:2009tm}. Long wave radiation
exchange between the simulated building and its surroundings is sent to
EnergyPlus; this process is describe\noteDT{s/describe/described/} in detail
in a subsequent methodology section\noteDT{can we not just name the section?
this phrasing seems awkward}. Finally, CitySim shares its calculated occupancy
schedules as it uses a more robust model of occupants behavior
\citep{Haldi:2011dr}.

% \noteDT{s/climactic/climatic/}
% \noteDT{this sentence, man. i can't even}

@@

Variables sent to CitySim by EnergyPlus at each time step include several
variables related to the calculation of heating and cooling loads of a
targeted building. These variables are transferred due to the ability of
EnergyPlus to model more detailed building systems, schedules, ventilation and
internal load types than CitySim. For example, EnergyPlus is flexible enough
to model a detailed, radiant heating and cooling system that would be
impossible in CiytSim \citep{barbara:2015tz}. EnergyPlus is an engine
optimized to accurately model building-scale systems, thus CitySim can take 
advantage of these models through coupling and co-simulation. EnergyPlus sends
the heating and cooling loads, the surface temperatures of the exterior
surfaces and the ventilation flow rates to CitySim.

%\noteDT{I'm not sure this is proper English. Or American for that
%matter...}

@@

In comparison, CitySim calculates LWR exchange by calculating an aggregated
equivalent temperature, $T_{env}$, and radiative heat transfer coefficient,
$h_{r,env}$, from surrounding urban surfaces in addition to ground, sky, and
air \citep{Robinson:2009tm}. The calculation for $T_{env}$ is expressed in
Equation \ref{CitySim_Tenv} with the $F$ values being view factors of the
surrounding environment including adjacent surfaces $i=1..n$. $h_{r,env}$ is
based on a first order Talyor development of the numerator of Equation
\ref{EPlus_h} around $(T_{surf}+T_{variable})/2$ and therefore
$Q_{LWR,CitySim}$ is calculated using Equation \ref{CitySim_LWR_Ext}.

\begin{equation} \label{CitySim_Tenv} 
\sigma T_{env}^4 = \sigma F_{sky}T_{sky}^4 +\sigma F_{grd}T_{grd}^4 + \sum_{i=1}^{n} \epsilon_i \sigma F_{i}T_{i}^4
\end{equation}
\begin{equation} \label{CitySim_LWR_Ext} 
Q_{LWR,CitySim} = h_{r,env}(T_{surf}-T_{env})
\end{equation}

@@

\subsection{Work flow automation}
The coupling, simulation and co-simulation process is completely managed
within a program called VisTrails \citep{Anonymous:Cayf2tu7}. This tool
empowers the coupling of various executable files and their connecting scripts
in graphical diagrams that enhances reproducibility and
process automation \citep{Freire:2014tt}.

% INSERT VISTRAILS GRAPHIC HERE\noteCM{Daren -- can you give me a good screenshot of the Vistrails for the HPI building? Pretty please.}\noteDT{sure - check out 36-HPI-cosim.pdf in the figures folder}

\begin{figure}[H]
  \centering
  \includegraphics[width=1.0\textwidth]{figures/36-cosim-HPI}
  \caption{Workflow in VizTrails
  \label{VizTrails}}
\end{figure}

\subsection{Simplified calibration}
In the first case study, one aspect of this analysis is the comparison of
actual measured performance of the target building on campus with the
simulation results of the co-simulation. A simplified calibration procedure is
adapted from previous research to compare the measured heating and cooling
data available on campus with various simulation scenarios
\citep{Samuelson:2015jg}. This calibration procedure was utilized in the
performance reconciliation of 18 buildings that were built according to the
LEED Canada protocol and were under review of actualized performance. This
protocol is unique in its analysis process to uncover design model
deficiencies in a step-wise manner, utilizing the most easily accessible
knowledge first and working towards equilibrium between measured and
simulated. An appropriate balance between effort of implementation and value
generated through the calibration process.

@@

\subsection{Campus case study 1: ETHZ Hoenggerberg Campus}
% {\color{red}This section will describe the ETH Hoenggerberg case study}
%The simulation and calibration process is implemented on a campus case study located in Z\"urich, Switzerland. 
The ETH Z\"urich Hoenggerberg campus includes 32 higher education facilities
 with spaces allocated to laboratories, office space, lecture halls,
 cafeterias, data centers and other types of similar spaces. The campus has a
 centralized energy management system (EMS) that contains 807 energy and water
 measurement points from heating, cooling, electricity, city gas, domestic hot
 water, grey water, and general water consumption. %\noteDT{deleted: "buildings"}

@@

The focus of the co-simulation process is that the performance of a targeted
building is evaluated through solo and coupled methods. The HPI building on
campus was chosen in this case study due to the amount and quality of measured
data available from the EMS for this building. HPI is a 2,610 sq. meter
building that is made up mostly of office space and classrooms. It also
includes 400 $m^2$ convenience store and coffee shop. The building is
indicated on a campus map shown in Figure \ref{fig:campusmap} and is shaded
red.

@@

\subsection{Model development}
In order to perform a co-simulation of the targeted buildings, initially a
CitySim model of the campus is developed. Through the workflow automation
process, this geometry was converted into an EnergyPlus input file as seen in
Figure \ref{fig:HPIcampus}. The EnergyPlus input file is then used as an input
to execute EnergyPlus solo and co-simulation processes for the purpose of
simplified calibration, and then to understand the magnitude of difference
between these simulation scenarios.% An existing EnergyPlus model is used for the HPZ building and simplified single-zone EnergyPlus models are extracted from the CitySim geometry for the other three targeted buildings.

@@

Energy data from the HPI building was collected and analyzed in the context of
the simplified calibration procedures. The measured datasets are screened and
aggregated into typical usage profiles to be used for the lighting, plug-
loads, and HVAC equipment availability schedules and power densities. Figure
\ref{fig:hpi_elec_profiles} illustrates the aggregation examples of electrical
energy for the HPI building. This profile was created through a filtering and
clustering process known as \emph{DayFilter} \citep{Miller:2015kr}. This
profile is used to set the availability schedules as inputs into the
EnergyPlus simulation to emulate the way occupants inhabit the building and
how the building management system (BMS) controls the lighting and HVAC
systems. 
% This approach is compared to the practice of interviews and site
% visits to determine such input parameters.\noteDT{where??? how??? i don't get
% it...}

@@

The measured and simulated data from both the co-simulation and EnergyPlus
solo simulation was compared in order to create a realistic scenario for
comparison. The calibration process was undertaken through a series of steps
such as including local weather conditions for the simulation period and
adding custom lighting schedules and power densities extracted from the
measured data. The models were calibrated to the summer season (May-September)
for cooling and the winter season (Jan-April and October to December) for
heating. This approach was taken as the data quality for the measurements were
deemed most accurate during the appropriate seasons. Figure
\ref{fig:hpi_measvssim} illustrates a comparison of the measured data with the
simulations after the tuning process. The final calibrated EnergyPlus solo
model had a normalized mean bias error (NMBE) of -9.36\% and a coefficient of
variation of root mean square error (CVRMSE) of 21.7\% for cooling and -9.36\%
and 29.4\% for heating. These metrics fall within the +/-10\% NMBE and +/-30\%
CVRSME used in this case study for the purposes of partial calibration. The
goal of calibration in this case is to simply bring the models to within a
reasonable range of reality in order to bring more confidence to analysis of
the discrepancies between the solo and co-simulation
scenarios.
%\noteDT{Clayton, can you introduce a consistency in the symbols for
% the figures? say, squares for co-simulation, circles for e+, triangles for
% measured? and do this across all the figures? small detail, but i think shows
% quality and a certain, how shall i call it? swissness? a qualité suisse?}
%Daily data was used to calculated goodness of fit to determine calibration success. 
%The final calibrated EnergyPlus solo model had a normalized mean bias error (NMBE) of -9.36\% and a coefficient of variation of root mean square error (CVRMSE) of 21.7\% for cooling and -9.36\% and 29.4\% for heating.

@@

\subsection{EnergyPlus co-simulation results}
After calibration, a comparison of co-simulation and solo EnergyPlus
simulations is made. For cooling, a discrepancy can be seen between co-
simulation and solo EnergyPlus. Co-simulation results in a 20.2\% decrease in
predicted cooling energy is observed as seen in Figure
\ref{fig:hpi_energypluscooling}. Figure \ref{fig:hpi_energyplusheating}
illustrates the difference in predicted heating energy consumption across the
test year. A consistent offset exists across the time frame of days in
January, the peak of the heating season. A more varied discrepancy across the
heating months is noticed resulting an overall increase of heating prediction
of 4.8\% due to co-simulation. The exchange of long wave radiation for this
particular site is substantial due to the proximity of surrounding buildings.
These performance differences due to co-simulation are compared to a
theoretical single-zone case study in which there was a 15-30\% increase in
heating energy and a 4-11\% decrease in cooling energy. The results from this
scenario are less extreme on the heating side and more on the cooling side.

% \noteDT{with respect to what???}
% \noteDT{greater than what??}

@@

With a particularly strong visual and formal identity, the SwissTech
Convention Centre (STCC) is clearly the key protagonist.\noteDT{move main
sentence to start of paragraph} Applied with important functions for the
region, the building has definitely become the new landmark. Designed as a
Minergie\noteDT{ref?} building, it includes modern energy conversion
technologies to reduce its energy consumption. The focus of the co-simulation
is realized on the STCC, simulated with the nearby buildings for housing,
retail and service areas.
